Changes in accessibility to food banks and food services during COVID-19 and implications for the food security of vulnerable populations in Hamilton, Ontario

### 2021-04-24 Accessibility-Foodbanks-Hamilton/Accessibility-Foodbanks-Hamilton.tex

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Changes in accessibility to food banks during COVID-19 and implications for the food security of vulnerable populations in Hamilton, Ontario},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{Changes in accessibility to food banks during COVID-19 and
implications for the food security of vulnerable populations in
Hamilton, Ontario}
    \author[Some University]{Author One\corref{1}}
   \ead{author1@example.com} 
    \author[]{Author Two}
   \ead{author2@example.com} 
    \author[Some University]{Author Three\corref{2}}
   \ead{author3@example.com} 
    \author[Another University]{Author Four\corref{2}}
   \ead{author4@example.com} 
      \address[Some University]{Department, Street, City, State, Zip}
    \address[Another University]{Department, Street, City, State, Zip}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

@@

Food insecurity is defined as an ``inadequate or uncertain access to a
sufficient quantity and/or adequate quality of food'' due to a
household's financial limitations (Enns et al., 2020). This condition
has been associated with reductions in nutritional outcomes
(Bhattacharya et al., 2004; Kirkpatrick and Tarasuk, 2008; Olson, 1999)
and physical and mental health in children and adults (Elgar et al.,
2021; Jones, 2017; Ramsey et al., 2011; Seligman et al., 2010; Stuff et
al., 2004). Over at least the past four decades food banks have become
an essential line of defense against food insecurity in Canadian
communities (Black and Seto, 2020; Holmes et al., 2018; Riches, 2002;
Tarasuk et al., 2020). In this respect, Canada is not unlike numerous
other wealthy countries where a systematic dismantling of the welfare
state took place in the intervening period (Tarasuk et al., 2014).

@@

In terms of geography, previous research conducted at the provincial
scale using data from the 2011-2012 CCHS found that the prevalence of
food insecurity ranged across the country from 11.8\% of households in
Ontario to 41\% of households in Nunavut (Tarasuk et al., 2019).
However, although previous research has examined the characteristics of
individuals and households accessing food banks, the locational or
transportation accessibility aspect of food bank access is not well
understood. A wealth of literature examining the food desert concept
suggests that, in addition to socio-economic and demographic factors,
location and transportation networks play a key role in a household's
accessibility to healthy foods (Paez et al., 2010; Vanderlee and L'Abbé,
2017; Widener, 2018). For food banks specifically, previous qualitative
research by Smith et al. (2017) in Ontario has noted that participants
access food banks using a variety of modes of transportation and that
some food bank users have expressed difficulties with transportation for
trips to food bank locations, with one respondent stating ``I wish it
{[}the food bank{]} was a little more centrally located. Because if I
didn't have a bike I'd have to walk it all the way out there and back. I
wonder about people who don't.'' From this, the authors conclude that
``transportation can be challenging, particularly if the food bank is
situated in a remote location.'' To offer greater insight into the role
of transportation and location in food bank accessibility, this research
examines how geographic accessibility to food banks and food services
changed in Hamilton during the COVID-19 pandemic.

@@

\noindent as is the level of service: \[
\sum_{j=1}^JL_jw_{ji}^\text{st}=L_j
\]

@@

The locations of food banks and related food services were obtained from
the Hamilton Public Library's Food Access Guide\footnote{http://foodaccessguide.ca/sites/default/files/partnersites/pdf/foodaccessguide.pdf}.
The guide was updated in April of 2021 to indicate any change affected
on the services due to the pandemic. This includes modified business
hours, a need to make reservations before frequenting, and locations
that have completely shut down in consequence. While some food bank
services have a specific a target population, such as prioritizing
family with young children aged between 0 and 3 or accepting only those
providing proof of low-income status through housing and utility
statements, all the food bank services indicated below are designed to
accommodate those in need of food at zero to low cost. With our focus on
food banks and food services that offer free or low-cost meals at
particular locations, we first removed services such as Meals on Wheels
and other food access services such as food box, community kitchens,
student nutrition programs, and shopping and transportation. In
addition, two free meal services held on different days at the same
location were collapsed into a single service point for the
accessibility analysis.

@@

Figure \ref{fig:foodbanks} shows the location of food banks in the City
of Hamilton and their status. Before the pandemic there were 58 of which
14 (24.14\%) closed during the pandemic. As shown in the figure, food
banks tend to be predominantly located in the central parts of the city.
This is not surprising: population density is high there, and it is also
the part of the city where lower income households are more numerous in
absolute and relative terms (see Figure
\ref{fig:low-income-households}). Alas, this is also the part of the
city where most of the closures during the pandemic happened.

\begin{figure}
\includegraphics[width=1\linewidth]{Accessibility-Foodbanks-Hamilton_files/figure-latex/plot-location-foodbanks-1} \caption{\label{fig:foodbanks}Location of foodbanks and operation status; the dotted box is an inset of the central part of the City of Hamilton}\label{fig:plot-location-foodbanks}
\end{figure}

@@

To implement the accessibility calculations, we must select a
distance-decay function. In this task we find limited support in the
literature, which is mostly silent on the travel patterns of people who
visit food banks. For this reason, we opt for a simple cumulative
opportunities function as follows: \[
w_{ij}=w_{ji}=
\begin{cases}
1 & \text{ if } ett_{ij}\le \delta\\
0 & \text{ otherwise}
\end{cases}
\] \noindent where \(ett_{ij}\) is the multimodal expected travel time
as described previously, and \(\delta\) is a travel threshold. When the
expected travel time exceeds this threshold, a facility is no longer
considered accessible. Further, the weights are standardized for the
balanced floating catchment area approach.

Figure \ref{fig:sensitivity-analysis} shows the results of conducting
sensitivity analysis of the system-wide accessibility as we vary the
threshold (considering the situation before the pandemic). There is a
clear pattern whereby more strict values of \(\delta\) are associated
with higher levels of system-wide accessibility: while increases in
accessibility that result from decreases in the travel time window might
seem counter-intuitive, this is a result of lower \emph{congestion},
since fewer households are serviced and are thus competing for the same
resources. System-wide accessibility declines with higher values of
\(\delta\): as more households are serviced, congestion grows and the
level of service declines, although this happens at a declining rate. We
are not aware of any standards that explain how long people are expected
to travel for food banks, but we note that in developing countries,
access to drinking water is defined as a source that takes less than 30
minutes to reach (round trip, see UNICEF-WHO, 2019). There is no reason
why people in affluent countries should be expected to travel more for a
basic need such as food. Accordingly, we adopt a threshold of 15 minutes
for the analysis (representing a one-way trip).

@@

Using this threshold, we find that the system-wide accessibility
(interpreted as a provider-to-population ratio) was 0.065 (food banks
and food service locations per low income household in the city) before
COVID-19, but declined to 0.037 during the pandemic. It is striking that
although almost 76\% of food banks remained in operation during the
pandemic, there was a loss of accessibility greater than 43\%,
suggesting the location of food banks and food services plays an
important role in serving those in need.

Turning to the individual food bank and food service locations, the
levels of service offered before and during the pandemic are shown in
Figure \ref{fig:levels-of-service}. The level of service is functionally
the inverse (because each food bank has a ``capacity'' of 1) of the
number of low-income households in the travel-mode weighted travel time
catchment area of the food banks. Higher values mean that a facility is
expected to service fewer households. Conversely, lower values indicate
grater congestion.

The general pattern of the levels of service is similar before and
during the pandemic, with lower values in the center of the city. Three
more peripheral facilities towards the south of the city also have lower
levels of service, presumably because they are meant to service a
relatively large suburban/exurban population. During the pandemic,
however, the levels of service dropped, in some cases quite
substantially. The pattern of the losses in level of service, moreover,
is not uniform. The upper pane of Figure
\ref{fig:levels-of-service-changes} shows that the three peripheral
facilities in the southern suburban/exurban part of the city had low
levels of service to begin with, but did not see major declines during
the pandemic. Turning to the inset map, levels of service deteriorated
more in the central part of the city. However, the loss of level of
service was not as large in the core (where most of the food banks are),
but more marked in the inner ring around the core where facilities may
have faced greater demand from both central city and suburban
populations after the closure of food banks during the pandemic.

@@

To further elucidate this issue, we now turn to the results of the
accessibility analysis. The top pane of Figure \ref{fig:accessibility}
reveals that, compared with the outer rural zones, the smaller more
urban zones of the city generally exhibit higher accessibility to food
banks and food service locations. However, the pattern is not
particularly smooth - this is largely attributable to the travel-mode
weighting of travel times according to the trip patterns of low-income
household respondents to the TTS. For example, in zones where low-income
households make a high proportion of trips by walking, access to food
bank locations by walking is afforded a concomitantly high weight in our
calculations of travel time compared to transit or car travel. From
this, highly-accessible locations result from a mix of characteristics:
low-income households in locations where travel options that align with
zonal modal split are available to connect them to food bank locations
with high levels of service within 15 minutes.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{Accessibility-Foodbanks-Hamilton_files/figure-latex/plot-local-i-1} \caption{\label{fig:plot-local-i}Changes in accessibility from pre-COVID-19 to during COVID-19. Highlighted areas had significantly large changes in accessibility according to Local Moran's I.}\label{fig:plot-local-i}
\end{figure}

@@

\caption{\label{tab:table-accessibility-by-age-group}\label{tab:accessibility-by-age}Accessibility by age group among members households with incomes less than CAD40,000.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{cccccc}
\toprule
\multicolumn{3}{c}{Population} & \multicolumn{3}{c}{Accessibility} \\
\cmidrule(l{3pt}r{3pt}){1-3} \cmidrule(l{3pt}r{3pt}){4-6}
Children (age $\le$ 18) & Adults (19-64) & Seniors (age $\ge$ 65) & Before COVID-19 & During COVID-19 & Difference\\
\midrule
\cellcolor{gray!6}{3,445} & \cellcolor{gray!6}{11,860} & \cellcolor{gray!6}{6,584} & \cellcolor{gray!6}{0.00229} & \cellcolor{gray!6}{0.00173} & \cellcolor{gray!6}{-0.00057}\\
4,477 & 12,838 & 6,847 & 0.00707 & 0.00418 & -0.00289\\
\cellcolor{gray!6}{3,541} & \cellcolor{gray!6}{13,189} & \cellcolor{gray!6}{7,020} & \cellcolor{gray!6}{0.01580} & \cellcolor{gray!6}{0.00911} & \cellcolor{gray!6}{-0.00669}\\
2,340 & 9,918 & 4,940 & 0.03985 & 0.02202 & -0.01783\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Population values have been rounded}\\
\end{tabular}}
\end{table}

@@

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-bazerghi2016role}{}%
Bazerghi, C., McKay, F.H., Dunn, M., 2016. The role of food banks in
addressing food insecurity: A systematic review. Journal of community
health 41, 732--740.

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Changes in accessibility to food banks and food services during COVID-19 and implications for the food security of vulnerable populations in Hamilton, Ontario},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{Changes in accessibility to food banks and food services during
COVID-19 and implications for the food security of vulnerable
populations in Hamilton, Ontario}
    \author[Some University]{Author One\corref{1}}
   \ead{author1@example.com} 
    \author[]{Author Two}
   \ead{author2@example.com} 
    \author[Some University]{Author Three\corref{2}}
   \ead{author3@example.com} 
    \author[Another University]{Author Four\corref{2}}
   \ead{author4@example.com} 
      \address[Some University]{Department, Street, City, State, Zip}
    \address[Another University]{Department, Street, City, State, Zip}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

@@

Food insecurity is defined as an ``inadequate or uncertain access to a
sufficient quantity and/or adequate quality of food'' due to a
household's financial limitations (Enns et al., 2020). This condition
has been associated with reductions in nutritional outcomes
(Bhattacharya et al., 2004; Kirkpatrick and Tarasuk, 2008; Olson, 1999)
and physical and mental health in children and adults (Elgar et al.,
2021; Jones, 2017; Ramsey et al., 2011; Seligman et al., 2010; Stuff et
al., 2004). Over at least the past four decades food banks and related
services have become an essential line of defense against food
insecurity in Canadian communities (Black and Seto, 2020; Holmes et al.,
2018; Riches, 2002; Tarasuk et al., 2020). In this respect, Canada is
not unlike numerous other wealthy countries where a systematic
dismantling of the welfare state took place in the intervening period
(Tarasuk et al., 2014).

@@

In terms of geography, previous research conducted at the provincial
scale using data from the 2011-2012 CCHS found that the prevalence of
food insecurity ranged across the country from 11.8\% of households in
Ontario to 41\% of households in Nunavut (Tarasuk et al., 2019).
However, although previous research has examined the characteristics of
individuals and households accessing food banks, the locational or
transportation accessibility aspect of food bank access is not well
understood. A wealth of literature examining the food desert concept
suggests that, in addition to socio-economic and demographic factors,
location and transportation networks play a key role in a household's
accessibility to healthy foods (Paez et al., 2010; Vanderlee and L'Abbé,
2017; Widener, 2018). For food banks specifically, previous qualitative
research in Ontario by Smith-Carrier et al. (2017) has noted that
``transportation can be challenging, particularly if the food bank is
situated in a remote location'' (p.~32). Particularly, it appears that
participants experience challenges with the ``inordinate amount of time
necessary to obtain food, and difficulties associated with
transportation'' (p.~39). Users of food banks, according to this
research, rely on a variety of modes of transportation to access
services. Consequently, the location of facilities matters; in the words
of an interviewee: ``I wish it {[}the food bank{]} was a little more
centrally located. Because if I didn't have a bike I'd have to walk it
all the way out there and back. I wonder about people who don't''
(p.~39).

To offer greater insight into the role of transportation and location in
food bank accessibility, this research examines how geographic
accessibility to food banks and food services changed in Hamilton during
the COVID-19 pandemic.

@@

\noindent as is the level of service: \[
\sum_{j=1}^JL_jw_{ji}^\text{st}=L_j
\] \#\# Study Area

\textbf{Need to provide some context here: the geography which makes
transportation challenging, i.e., due to the escarpment; the main parts
of the city: city core, inner suburbs, industrial north, suburban,
exurban; and the industrial background of the city maybe, with poverty
rates compared to other Canadian cities?}

@@

The locations of food banks and related food services were obtained from
the Hamilton Public Library's Food Access Guide\footnote{http://foodaccessguide.ca/sites/default/files/partnersites/pdf/foodaccessguide.pdf}.
The guide was updated in April of 2021 to indicate any change affected
on the services due to the pandemic. This includes modified business
hours, a need to make reservations before frequenting, and locations
that have completely shut down in consequence. While some food bank
services have a specific a target population, such as prioritizing
family with young children aged between 0 and 3 or accepting only those
providing proof of low-income status through housing and utility
statements, all the food bank services indicated below are designed to
accommodate those in need of food at zero to low cost. With our focus on
food banks and food services that offer free or low-cost meals at
particular locations, we first removed services such as Meals on Wheels
and other food access services such as food box, community kitchens,
student nutrition programs, and shopping and transportation. In
addition, two free meal services held on different days at the same
location were collapsed into a single service point for the
accessibility analysis. Additional details on the operations of
individual facilities is not publicly available, and with the changes in
operations it proved unfeasible to collect it. For this reason, the
analysis to follow is of accessibility to the location of food banks and
services, but not to specific services (e.g., breakfasts vs.~food
boxes).

@@

Figure \ref{fig:foodbanks} shows the location of food banks and services
in the City of Hamilton and their status. Before the pandemic there were
58 of which 14 (24.14\%) closed during the pandemic. As shown in the
figure, food services tend to be predominantly located in the central
parts of the city. This is not surprising: population density is high
there, and it is also the part of the city where lower income households
are more numerous in absolute and relative terms (see Figure
\ref{fig:low-income-households}). Alas, this is also the part of the
city where most of the closures during the pandemic happened.

\begin{figure}
\includegraphics[width=1\linewidth]{Accessibility-Foodbanks-Hamilton_files/figure-latex/plot-location-foodbanks-1} \caption{\label{fig:foodbanks}Location of food banks/services and operation status; the dotted box is an inset of the central part of the City of Hamilton}\label{fig:plot-location-foodbanks}
\end{figure}

@@

To implement the accessibility calculations, we must select a
distance-decay function. In this task we find limited support in the
literature, which is mostly silent on the travel patterns of people who
visit food banks. For this reason, we opt for a simple cumulative
opportunities function as follows: \[
w_{ij}=w_{ji}=
\begin{cases}
1 & \text{ if } ett_{ij}\le \delta\\
0 & \text{ otherwise}
\end{cases}
\] \noindent where \(ett_{ij}\) is the multimodal expected travel time
as described previously, and \(\delta\) is a travel threshold. When the
expected travel time exceeds this threshold, a facility is no longer
considered accessible. Moreover, the weights are standardized for the
balanced floating catchment area approach.

Figure \ref{fig:sensitivity-analysis} shows the results of conducting
sensitivity analysis of the system-wide accessibility as we vary the
threshold (considering the situation before the pandemic). There is a
clear pattern whereby more strict values of \(\delta\) are associated
with higher levels of system-wide accessibility: while increases in
accessibility that result from decreases in the travel time window might
seem counter-intuitive, this is a result of lower \emph{congestion},
since fewer households are serviced and thus competition for the same
resources is more limited. System-wide accessibility declines with
higher values of \(\delta\): as more households are serviced, congestion
grows and the level of service declines, although this happens at a
declining rate. We are not aware of any research that explain how long
people are expected to travel for food banks, but we note that in
developing countries, access to drinking water is defined as a source
that takes less than 30 minutes to reach (round trip, see UNICEF-WHO,
2019). There is no reason why people in affluent countries should be
expected to travel more for a basic need such as food. Accordingly, we
adopt a 15-minute threshold for the analysis (representing a one-way
trip). This threshold is also approximately where the rate of change in
accessibility slows down.

@@

Using the 15-minute threshold, we find that the system-wide
accessibility (interpreted as a provider-to-population ratio) was 0.065
(food banks/service locations per low income household in the city)
before COVID-19, but declined to 0.037 during the pandemic. It is
striking that although almost 76\% of food facilities remained in
operation during the pandemic, there was a loss of accessibility greater
than 43\%, suggesting the location of food banks and related services
plays an important role in serving those in need.

Turning to the location of individual facilities, the levels of service
offered before and during the pandemic are shown in Figure
\ref{fig:levels-of-service}. The level of service is functionally the
inverse of the number of low-income households in the travel-mode
weighted travel time catchment area of the facilities (this is because
\(S_j=1 \forall j\), i.e., each location represents a ``capacity'' of
1). Higher values mean that a facility is expected to service fewer
households. Conversely, lower values indicate grater congestion.

The general pattern of the levels of service is similar before and
during the pandemic, with lower values in the center of the city. Three
more peripheral facilities towards the south of the city also have lower
levels of service, presumably because they are expected to service
relatively large suburban/exurban populations. During the pandemic,
however, the levels of service dropped, in some cases quite
substantially. The pattern of the losses in level of service, moreover,
is not uniform. The upper pane of Figure
\ref{fig:levels-of-service-changes} shows that the three peripheral
facilities in the southern suburban/exurban part of the city had low
levels of service to begin with, but did not see major declines during
the pandemic. Further, the inset map shows that the levels of service
deteriorated more in the central part of the city. However, the loss of
level of service was not as large in the core (where most of the food
banks/services are found), but instead was more marked in the inner ring
around the core, where facilities may have faced greater demand from
both central city and suburban populations after the closure of food
banks during the pandemic.

@@

To further elucidate this issue, we now turn to the results of the
accessibility analysis. As with the level of service of individual
facilities, the general pattern of accessibility before and during the
pandemic is similar. Figure \ref{fig:accessibility} reveals that,
compared with the outer rural zones, the more urban zones of the city
generally exhibit higher accessibility to food banks and food service
locations. However, the pattern is not particularly smooth - this is
largely attributable to the weighting of travel times by mode of
transportation according to the trip patterns of low-income household
respondents according to the TTS. For example, in zones where low-income
households make a high proportion of trips by walking, access to food
bank locations by walking is afforded a concomitantly high weight in our
calculations of travel time compared to transit or car travel. From
this, highly-accessible locations result from a mix of characteristics:
low-income households in locations where travel options that align with
zonal modal split are available to connect them to food bank locations
with high levels of service within 15 minutes. This seems to track with
the experience of some users of these services, as reported by
Smith-Carrier et al. (2017).

@@

We find that the accessibility landscape deteriorated substantially
during the pandemic, with accessibility dropping on average by almost
41\%, but with large variations: some zones experienced changes in
accessibility of only about 10\%, whereas the most affected zone saw a
loss of accessibility of almost 71\%. Figure
\ref{fig:accessibility-changes-with-local-i} shows the changes in
accessibility. Every zone is worse off after the closure of facilities
during the pandemic, but some parts of the city seem to have been
particularly affected. We used a local indicator of spatial
autocorrelation (Anselin, 1995) to explore the pattern of change in
accessibility. Twenty-four TAZ are flagged as having significant large
losses of accessibility (at \(p<=0.10\), without correcting for multiple
comparisons). Those zones are highlighted in the figure, where it can be
seen that they form more or less compact neighborhoods. Remarkably, the
largest (and significant) drops in accessibility are not downtown, but
located in two cases in the industrial north of the city, in one case in
an inner suburb above the escarpment (\textbf{need to describe the study
area!}), and lastly in a more suburban/exurban region in the south-west
(\textbf{share other insights about these regions, maybe based on
weighted travel patterns?}).

\begin{figure}
\includegraphics[width=1\linewidth]{Accessibility-Foodbanks-Hamilton_files/figure-latex/plot-local-i-1} \caption{\label{fig:accessibility-changes-with-local-i}Changes in accessibility from pre-COVID-19 to during COVID-19. Highlighted areas had significantly large changes in accessibility according to Local Moran's I.}\label{fig:plot-local-i}
\end{figure}

@@

\caption{\label{tab:table-accessibility-by-age-group}\label{tab:accessibility-by-age}Accessibility by age group among members households with incomes less than CAD40,000.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{cccccc}
\toprule
\multicolumn{3}{c}{Population} & \multicolumn{3}{c}{Accessibility} \\
\cmidrule(l{3pt}r{3pt}){1-3} \cmidrule(l{3pt}r{3pt}){4-6}
Children (age $\le$ 18) & Adults (19-64) & Seniors (age $\ge$ 65) & Before COVID-19 & During COVID-19 & Difference\\
\midrule
\cellcolor{gray!6}{3,445 (25\%)} & \cellcolor{gray!6}{11,860 (24.8\%)} & \cellcolor{gray!6}{6,584 (25.9\%)} & \cellcolor{gray!6}{0.00229} & \cellcolor{gray!6}{0.00173} & \cellcolor{gray!6}{-0.00057}\\
4,477 (32.4\%) & 12,838 (26.9\%) & 6,847 (27\%) & 0.00707 & 0.00418 & -0.00289\\
\cellcolor{gray!6}{3,541 (25.7\%)} & \cellcolor{gray!6}{13,189 (27.6\%)} & \cellcolor{gray!6}{7,020 (27.6\%)} & \cellcolor{gray!6}{0.01580} & \cellcolor{gray!6}{0.00911} & \cellcolor{gray!6}{-0.00669}\\
2,340 (17\%) & 9,918 (20.7\%) & 4,940 (19.5\%) & 0.03985 & 0.02202 & -0.01783\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Population values have been rounded}\\
\end{tabular}}
\end{table}

@@

\textbf{LIMITATIONS}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-anselin1995local}{}%
Anselin, L., 1995. Local indicators of spatial association - LISA.
Geographical Analysis 27, 93--115.

\leavevmode\hypertarget{ref-bazerghi2016role}{}%
Bazerghi, C., McKay, F.H., Dunn, M., 2016. The role of food banks in
addressing food insecurity: A systematic review. Journal of community
health 41, 732--740.
